---
title: "parameters"
---

## Estimates

### Adult survival

Amtech adulat/subadult survival: logit = -0.5738307, sd = 0.2515

survival = 0.36

Ring tanks: 40 initial with 32 surviving two years; 32/40 = 0.8

sqrt(0.8) = yearly survival 0.89

### Juvenile survival

second year hatchlings = 25 with 10-15 surviving

Optimistic juvenile survival = 0.6

Pessimistic juvenile survival = 0.15 (from Wendy Dimonds PVA 0.334<sub>summer</sub> 0.443<sub>winter</sub> juvenile survival)

### Transition

transition to SA = 0.194 (from Wendy Dimonds PVA)

### Reproduction

fecundity unknown

We will estimate percent of females reproducing using a uniform prior ranging 0 to 1. However, this will ideally be refined based on ring tank data of offspring relatedness.

clutch size = 5.5 with a range of 4 to 7 (from Wendy Dimonds PVA where she uses a beta(2) distribution)

Changed to range of 3-7 with a beta distribution of beta(2,3) based on captive colony (UC)

### Environmental Stoch

Tried to use NDVI and LST but did not have enough predictive power - so envrionmental stochasticity will be estimated separately to all other parameters.

### Carrying capcity

off handidly set to 50/hectare based on something Brett said in a meeting.

Changed to 60/hectare based on max abundance estimates from 2006 at JW

### Model fitting

We will used mean squared difference to optimise our model paramters.

## Model parameters

```{r message=FALSE, warning=FALSE}
source('./code/04_parameters.R')
paramter_fxtb

```

### Parameter distributions

```{r fig.width=10, fig.height=12}
distribution_fig
```

### Stage matrix

We define a stage matrix to help with defining starting stage distributions from initial adult abundance estimates.

```{r}
stagemat_lambda
fx_stages

```

### Transition matrix

```{r}
fx_transition # transition matrix following survival

```
